---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# tidysim

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/coatless/tidysim.svg?branch=master)](https://travis-ci.org/coatless/tidysim)
[![CRAN status](https://www.r-pkg.org/badges/version/tidysim)](https://cran.r-project.org/package=tidysim)
<!-- badges: end -->

The goal of `tidysim` is to provide tools for manipulating simulation data 
into a tidy format.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("coatless/tidysim")
```

## Examples

The common task when running simulation studies is to estimate parameters
underneath a specific method and then compare the results. Estimated parameter
data is stored in a `matrix` with each simulation iteration taking a column
and each variable estimation taking a row or vice versa. 

```{r demo-load-sim}
# Set Seed
set.seed(5812)
# Generate data
my_sim = matrix(rnorm(8), nrow = 2, ncol = 4)

# Apply labels
rownames(my_sim) = c("Beta0", "Beta1")
colnames(my_sim) = paste0("Sim", seq_len(ncol(my_sim)) )

# Example data
my_sim
```

Data stored in this manner is problematic as it isn't easily graphable under
a tidy approach.  


Within `tidysim`, the simulation matrix is converted into a
tidy `data.frame`.  The `Round` variable indicates the simulation number
and the `Parameter` variable stores the parameter being estimated. Once the
data is generated, it can be coerced into the appropiate shape with
`sim_df(..., wide)`, where `wide` denotes whether to treat the simulation
data as having repeated estimates for parameter estimates given in the columns
or stored row-wise.

```{r show-wide-sim}
# Load package
library("tidysim")

# Organize by row
my_sim_from_wide = sim_df(my_sim, wide = TRUE)

# View first 5 rows
head(my_sim_from_wide, n = 5)

autoplot(my_sim_from_wide)
```


## Authors

James Joseph Balamuta and David Dalpiaz

## License

GPL (>= 2)
