---
title: "An Overview of `tidysim`: Tidy Simulation"
author: "James Balamuta"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tidy-simulation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Intro

The package houses different functions to allow for tidy simulation data.

With this being said, to use the package, first install it via either CRAN or
GitHub:

```{r install-pkg, eval = FALSE}
# install.packages("devtools")
devtools::install_github("coatless/tidysim@*release")
install.packages("tidysim")
```

Then load it via:

```{r load-tidysim}
library("tidysim")
```

You may wish at times to use functions within this package that collide with 
similarly named functions in other packages. To do so, please prefix function 
calls by `tidysim::`.

# Utilities

The package hosts various utilities to improve working with simulated data.

In particular, the package offers the ability to cast a simulation `matrix` to
`data.frame` for graphing within `ggplot2`. The simulation cast feature is
meant to ease the use of simulated data within `ggplot2`. Thus, support exists
for both casting simulated data stored by row (default) and by column into a
`Round` and `Draw` framework, where `Round` means the simulation iteration and
`Draw` means the statistic observed.

```{r simulation_objects}
# Set Seed
set.seed(5812)
# Generate data
m = matrix(rnorm(10), 2, 5)

# Organize by row
wide_m = sim_df(m)
# View first 5 rows
head(wide_m, n = 5)

# Organize by column
long_m = sim_df(m, wide = FALSE)
# View first 5 rows
head(long_m, n = 5)

# Graph wide
autoplot(wide_m)
# Graph long
autoplot(long_m)
```
